Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
intro: BDD also includes test discovery and continuous integration

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.  BDD
includes TDD, amongst other software development methods, but
with a terminology and mindset  shifted towards specification instead
of testing.  In BDD, specifications can be used for automatic testing.

@@

\begin{quote}
    \emph{sol: @mkl, any idea where to put this?}

\emph{Automation, such as test discovery and continuous integration (CI)
~\cite{ci} is an important aspect of BDD.}
\end{quote}

>>>>

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.  BDD
includes TDD, but with a terminology and mindset  shifted towards
specification instead of testing. BDD also includes other software
development methods, such as automatic test discovery and continuous
integration~\cite{ci}.  In BDD, specifications can be used for
automatic testing.

@@
